Compact and widely bandwidth-tunable silicon filter with an unlimited free-spectral range

### 2015-10-22 ReviewersReply.tex

\emph{Large coupling coefficients and precise apodization profiles are easier to achieve with this process, although optical lithography able to resolve the required periodicity and gap between waveguides as seen in Fig.~2~a) could be used. The corrugations do not need to be square shaped, but must have a large enough amplitude.}

\emph{Our experience with optical lithography shows that the design needs to be biased to account for amplitude distortion, but it is in principle possible to use CMOS compatible process, albeit with an additional iteration to obtain the biasing information.}

\item A brief discussion on the coupling coefficients and \textbf{radiation losses} of the contra-directional couplers may be appropriate. We assume that the coefficients play a large role in obtaining the filter shapes present.

\emph{High coupling coefficients are necessary to design short devices with low through port losses and large bandwidth. A comparison with the fabricated device versus a larger coupling is illustrated in Fig. 7. Comment on losses with the reference \cite{caverley2015measurement}}

@@

\item Following from the foregoing two points, we notice a 2-dB insertion loss in Fig. 3. Is this a result of radiation loss or large amounts of signal exiting from the “through” and “residue” ports?

\emph{Fig. 3 shows an insertion loss of 0.5 dB, both in experiments and in simulation. This loss is  mainly due to silicon absorption and waveguide radiative losses (0.4 dB). The signal exiting from other ports causes about 0.1 dB of losses.}

\item We encourage the authors to drop the term “ultra-compact” from their title. By the authors’ own admission, the device is at least 312 µm long, with at least several microns of width. These dimensions may be compact in terms of conventional optical filters, but in a silicon platform, which tends to promise large-scale integrability of components, these dimensions are far from compact.

\emph{The device ($\approx$ 7,000 \textmu m$^2$) is about hte same size as micro-rings ( also $\approx$ 7,000 \textmu m$^2$) and smaller than most MZI designs($\approx$ 600,000 \textmu m$^2$) with similar performance. Changed to "Compact" }
\end{itemize}

### 2015-10-22 CacadedTunableFilter.tex
Update from Wei meeting

\title{Ultra-compact, widely bandwidth-tunable silicon filter with an unlimited free-spectral range}

@@

\begin{abstract}
Next-generation high-capacity optical networks require flexible allocation of spectrum resources, for which low-cost optical filters with an ultrawide bandwidth tunability beyond hundred GHz are desired.
We demonstrate an integrated band-pass filter with the bandwidth continuously tuned across 670 GHz (117 GHz to 788 GHz), which, to the best of our knowledge, is the widest tuning span ever demonstrated on a silicon chip.
The filter also features simultaneous wavelength tuning and an unlimited free spectral range. 
We measured an out-of-band contrast of up to 55 dB, low in-band ripples of less than 0.3 dB, and in-band group delay variation of less than 8 ps.
This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7000~\textmu m$^2$. Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented. 
\end{abstract}

@@

For improved performance and flexibility, more stages can be cascaded.
Fig.~\ref{fig:bandTuneSimu} shows our simulation results of a 4-stage cascade contra-DC filter, consisting of two pairs of identical contra-DCs with a stronger coupling than the one experimentally demonstrated (53500~m$^{-1}$ vs 38000~m$^{-1}$). Each pair is controlled by the same temperature, performing as a single tuning element.

>>>>

\title{Compact and widely bandwidth-tunable silicon filter with an unlimited free-spectral range}

@@

\begin{abstract}
	Next-generation high-capacity optical networks require flexible allocation of spectrum resources, for which low-cost optical filters with an ultrawide bandwidth tunability beyond hundred GHz are desired.
	We demonstrate an integrated band-pass filter with the bandwidth continuously tuned across 670 GHz (117 GHz to 788 GHz), which, to the best of our knowledge, is the widest tuning span ever demonstrated on a silicon chip.
	The filter also features simultaneous wavelength tuning and an unlimited free spectral range. 
	We measured an out-of-band contrast of up to 55 dB, low in-band ripples of less than 0.3 dB, and in-band group delay variation of less than 8 ps.
	This result was achieved using cascaded Bragg-grating-assisted contra-directional couplers and micro-heaters on the 220-nm silicon-on-insulator platform with a footprint of less than 7,000~\textmu m$^2$. Another design with the bandwidth continuously tunable from 50 GHz to 1 THz is also presented. 
\end{abstract}

@@

	For improved performance and flexibility, more stages can be cascaded.
	Fig.~\ref{fig:bandTuneSimu} shows our simulation results of a 4-stage cascade contra-DC filter, consisting of two pairs of identical contra-DCs with a stronger coupling than the one experimentally demonstrated (53.5~mm$^{-1}$ vs 38~mm$^{-1}$). Each pair is controlled by the same temperature, performing as a single tuning element.
